Face Attractiveness and the Sense of Reality

### 2022-08-25 analysis.Rmd
update

### Error Rate

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  summarize(
    # n = n(),
    Error = sum(Error) / n(),
    RT_Mean = mean(RT),
    RT_SD = sd(RT),
    IPIP6_SD = mean(IPIP6_SD),
    PID5_SD = mean(PID5_SD),
  ) |>
  ungroup() |>
  arrange(desc(Error))

data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm=TRUE))) |> 
  rbind(dfsub) |> 
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |> 
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A") |> 
  kableExtra::row_spec(which(dfsub$Participant %in% partial_outliers) + 1, background = "#FFECB3")
```

@@

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, Age, Sex, Ethnicity, Education, Nationality, Device_OS, starts_with("Screen")) |>
  slice(1) |>
  ungroup()
```

@@

@@

>>>>

### Attention Checks

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, starts_with("Attention")) |> 
  slice(1) |> 
  ungroup() |>
  mutate(Attention_Check = mean(c(Attention_Check1, Attention_Check2, Attention_Check3))) |> 
  arrange(Attention_Check)
```

### Duration

```{r message=FALSE, warning=FALSE}

### Ratings

```{r message=FALSE, warning=FALSE}
dfsub$Cor_Trustworthy <- NA
dfsub$Cor_Attractive <- NA
for(participant in dfsub$Participant) {
  dfsub[dfsub$Participant == participant, "Cor_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
  dfsub[dfsub$Participant == participant, "Cor_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
}
```

```{r message=FALSE, warning=FALSE}
data.frame(Participant = c("Total"), t(sapply(dfsub[2:ncol(dfsub)], mean, na.rm=TRUE))) |> 
  rbind(dfsub) |> 
  knitr::kable() |>
  kableExtra::row_spec(1, italic = TRUE) |> 
  kableExtra::row_spec(which(dfsub$Participant %in% outliers) + 1, background = "#EF9A9A")
```

@@

```{r message=FALSE, warning=FALSE}
dfsub <- df |>
  group_by(Participant) |>
  select(Participant, Age, Sex, Sexual_Orientation, Ethnicity, Education, Nationality, Device_OS, starts_with("Screen")) |>
  slice(1) |>
  ungroup()
```

@@

p5 <- plot_waffle(dfsub, "Sexual_Orientation")

@@

## Results

### Manipulation Check

```{r message=FALSE, warning=FALSE}
df |> 
  ggplot(aes(x = Real, y = Participant, fill=Participant)) +
  ggdist::stat_slab(scale=2, slab_alpha = 0.9) + 
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(limits = c(-100, 100), 
                     expand = c(0.01, 0.01),
                     breaks = c(-100, 0, 100),
                     label = c("Fake", "0", "Real")) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title= "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face = "bold", hjust = 0.5))
```

### Simulation Monitoring
